\documentclass[a4paper,man,natbib,floatsintext,12pt]{apa7}

\usepackage[english]{babel} %character and hyphenation rules specific to the language you choose
%\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{tabularx} %great for APA-style Tables
\usepackage{siunitx} % Required for good table alignmen
\sisetup{
  round-mode          = places, % Rounds numbers
  round-precision     = 2, % to 2 places
}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{wrapfig}
\usetikzlibrary{shapes,decorations,arrows,calc,arrows.meta,fit,positioning}
\tikzset{
    -Latex,auto,node distance =1 cm and 1 cm,semithick,
    latent/.style ={ellipse, draw, minimum width = 0.7 cm},
    observed/.style ={rectangle, draw},
    bidirected/.style={Latex-Latex,dashed},
    el/.style = {inner sep=2pt, align=left, sloped}
}
\newcommand{\sigFtest}[4]{\textit{F}(#1,#2) = #3, \textit{p}$<$#4}
\newcommand{\nonsigFtest}[3]{\textit{F}(#1,#2) = #3, \textit{p}$>$.05}


\title{Examining Emotional and Psychological Outcomes of a Modified Tuning in to Teens\textsuperscript{®} Program}
\shorttitle{Emotional and Psychological Outcomes of TINT}
\author{Natalie Tuinstra}
\affiliation{College of William \& Mary}
\journal{The Best Psychology Journal EVER!}
\abstract{Early adolescence is a key developmental stage during which symptoms of anxiety, depression, and behavioral difficulties often intensify. Emotional competency skills, such as awareness, expression, and coping, play a vital role in mitigating these risks. The present study examined the effects of a modification of the Tuning in to Teens® (TINT) program (Kehoe et al., 2014), traditionally designed for parents, but now adapted for direct involvement of a community sample of middle-school-age adolescents. Participants were 45 youth (Mage= 11.79 years; 57.8\% girls; 75.6\% White) who participated in six weekly, two-hour group sessions focused on teaching emotional competency skills related to anger, sadness, and worry. Adolescents and their caregivers completed emotion skills and psychopathology measures at baseline (T1), post-intervention (T2), and one-month follow-up (T3). Adolescents reported significant improvements in emotion regulation coping and reductions in internalizing and externalizing symptoms. Parents observed gains in emotional awareness, expression, and regulation, along with fewer externalizing behaviors. Emotion-specific patterns emerged: across time, worry was more inhibited than anger and sadness, yet more effectively regulated. In contrast, anger and sadness were more likely to be expressed in dysregulated ways and less likely to demonstrate consistent improvement in regulation. These findings offer preliminary evidence for the short-term benefits of this modified TINT program that appears to support adolescent emotional and psychological well-being.}
\keywords{intervention, emotion regulation, psychopathology}
\authornote{I would like to thank my dog, George, for taking a nap while I worked on this.}
\leftheader{Alternate page header in man mode}

%-------------- END PREAMBLE  -------------------


\begin{document}

\maketitle  %Insert my APA style title page

\input{intro.tex}

\input{method.tex}

\input{results.tex}

\input{discussion.tex}


\bibliography{references.bib}

\end{document}